\documentclass[12pt]{article}

\input{defaultPream}

% double space
\usepackage{setspace}
\doublespace

\usepackage{verbatim}

\begin{document}

\section{Summary}

\qq The following is a comprehensive account of the contents and possible events
of each room. Features that were planned, but were ultimately unimplemented, are
marked with a '$\ast$'.

%----------BEGIN BRIDGE----------

\subsection{Bridge}

\qq The starting location of the player.

\begin{enumerate}
  \item \textbf{Consoles}: May be looked at to reveal the following:
  \begin{enumerate}
    \item \textbf{Navigation Controls}: May be looked at.
    \begin{enumerate}
      \item \textbf{Joystick}: May be looked at. Nothing happens.
    \end{enumerate}
    \item \textbf{System Controls}: May be looked at.
    \begin{enumerate}
      \item \textbf{Light Controls}: Controls the ship's lights. Turning them
        off prevents the player from looking at anything.
      \item \textbf{Door Controls}: Controls that lock and unlock the ship's
        doors. Locking the doors prevents the player from leaving the bridge.
      \item \textbf{Cargo Bay Airlock Controls}: Controls that open and close
        the cargo bay airlock.
    \end{enumerate}
  \item \textbf{Communication Controls}: Controls that can be rigged to emit a
    static that may cause
    passing ships to stop and investigate. Necessary for the scavenging ship to stop
    and hail, otherwise
    it will pass by and the player will be unable to repair the engine. If it is
    rigged, then at between 20 
    and 35 (in-game) minutes the scavenging ship will attempt to hail the ship. If
    the player is at the comms, they may be answered, causing the scavenging ship
    to dock and its crew to board the ship. 
  \end{enumerate}
  \item \textbf{Ladder}$\ast$: A ladder leading down to an airlock that would have
    allowed for space walks.
\end{enumerate}

%-----------END BRIDGE-----------

%----------BEGIN FRONT HALL----------

\subsection{Front Hall}

\begin{enumerate}
  \item \textbf{Ladder}: May be looked at.
  \begin{enumerate}
    \item \textbf{Oxygen Controls}$\ast$: Controls that would have been able to
      restrict or cut off the flow of oxygen throughout the ship.
    \item \textbf{Temperature Controls}$\ast$: Controls that would have been
      able to restrict the temperature regulation of the ship.
  \end{enumerate}
\end{enumerate}

%-----------END FRONT HALL-----------

%----------BEGIN KITCHEN----------

\subsection{Kitchen}

\begin{enumerate}
  \item \textbf{Cabinets}: May be looked at.
  \begin{enumerate}
    \item \textbf{Food}: A purely cosmetic item.
    \item \textbf{Cutlery}$\ast$: Items that would have enabled close-quarters
      grappling with the scavenging crew.
  \end{enumerate}
  \item \textbf{Table}: May be looked at.
  \begin{enumerate}
    \item \textbf{Cutlery}$\ast$: Items that would have enabled close-quarters
      grappling with the scavenging crew.
  \end{enumerate}
\end{enumerate}

%-----------END KITCHEN-----------

%----------BEGIN BACK HALL----------

\subsection{Back Hall}

\begin{enumerate}
  \item \textbf{Ladder}: May be looked at.
  \begin{enumerate}
   \item \textbf{Airlock}$\ast$: A hatch that would have allowed for space
     walks.
   \item \textbf{Gravity Rotor}$\ast$: The rotor controlling the artificial
     gravity on the ship. Would have been made adjustable to affect ship
     navigation and interactions with the scavenging crew.
  \end{enumerate}
\end{enumerate}

%-----------END BACK HALL-----------

%----------BEGIN ENGINE ROOM----------

\subsection{Engine Room}

\begin{enumerate}
  \item \textbf{Engine}: The initially broken engine. If examined or diagnosed
    while the player has either read the manual or succeeded on a 1 in 4 chance,
    the player can determine that the calalyzer is broken. When attempting to
    repair the engine, if the player has the catalyzer in inventory, the game is won.
  \item \textbf{Engine Bins}: May be looked at.
  \begin{enumerate}
    \item \textbf{Tools}: A cosmetic item.
    \item \textbf{Parts}: A cosmetic item.
    \item \textbf{Manual}: A technical manual that, when read, gives the player
      knowledge about the engine. It tells the player that the catalyzer is the
      part that needs to be found.
  \end{enumerate}
\end{enumerate}

%-----------END ENGINE ROOM-----------

%----------BEGIN CREW DORMS----------

\subsection{Crew Dorms}

\begin{enumerate}
  \item \textbf{Ladder}: A cosmetic item.
  \item \textbf{Weapons}: Guns that can be used for defense should the
    scavenging crew board. If the player does not have a gun in inventory when
    the scavenging crew boards, the player will surely die.
  \item \textbf{Food}: A cosmetic item.
  \item \textbf{Clothing}$\ast$: Item that would have allowed the player to survive
    longer in the ship once the temperature had dropped below a certain point.
\end{enumerate}

%-----------END CREW DORMS-----------

%----------BEGIN CATWALK----------

\subsection{Catwalk}

\qq If the player enters the catwalk when the airlock is open and the scavenging
ship has not docked, they will be sucked out into space.

%-----------END CATWALK-----------

%----------BEGIN CARGO BAY----------

\subsection{Cargo Bay}

\qq If the player enters the cargo bay when the airlock is open and the
scavenging ship has not docked, then they will be sucked out into space. If the
player opens the airlock while the scavenging ship has docked, then the crew
will board and pull their guns on the player. Any action will cause the captain
to shoot the player in one of four locations: the head, chest, stomach, or
legs. A head or chest injury results in instant death. If the player is shot in
the stomach or legs and has picked up a weapon, then they will surprise the
captain, who orders a retreat after giving the player a spare catalyzer; the
crew then undocks and leaves. If the player does not have a gun, the captain
shoots the player again, killing them.

\begin{enumerate}
  \item \textbf{Boxes}: May be looked at.
  \begin{enumerate}
    \item \textbf{Weapons}: Guns that can be used for defense should the
    scavenging crew board. If the player does not have a gun in inventory when
    the scavenging crew boards, the player will surely die.
    \item \textbf{Parts}$\ast$: Spare parts that would have had a random chance
      of containing a catalyzer
  \end{enumerate}
  \item \textbf{Space Suit}: A suit that the player may wear. If the player is
    sucked out into space while wearing the suit, they will tumble about for a
    short while before succumbing to their fate.
  \item \textbf{Airlock Switch}: A switch that opens and closes the cargo bay
    airlock. If the call of the scavenging ship had been answered, opening the
    airlock triggers the boarding sequence. Otherwise, the player is sucked out
    into space.
\end{enumerate}

%-----------END CARGO BAY-----------

%----------BEGIN INFIRMARY----------

\subsection{Infirmary}

\begin{enumerate}
  \item \textbf{Cabinets}: May be looked at.
  \begin{enumerate}
    \item \textbf{Biofoam}$\ast$: A fast acting wound sealant that would have
      allowed the player to last longer after sustaining injuries.
    \item \textbf{Bandages}$\ast$: A wound sealant that would have allowed the
      player to last longer after sustaining injuries.
    \item \textbf{Painkillers}$\ast$: Pills that would have allowed the player
      to act normally after sustaining injuries.
    \item \textbf{Adrenaline}$\ast$: A shot that would have temporarily restored
      the player's health.
  \end{enumerate}
  \item \textbf{Tables}
  \begin{enumerate}
    \item \textbf{Dope}$\ast$: A sedative that would have knocked out the player
      for several hours.
    \item \textbf{Syringes}: A cosmetic item.
    \item \textbf{Surgical Tools}: A cosmetic item.
  \end{enumerate}
\end{enumerate}

%-----------END INFIRMARY-----------

%----------BEGIN PASSANGER DORMS----------

\subsection{Passenger Dorms}

\begin{enumerate}
  \item \textbf{Dressers}
  \begin{enumerate}
    \item \textbf{Food}: A cosmetic item.
    \item \textbf{Clothing}$\ast$: Item that would have allowed the player to survive
    longer in the ship once the temperature had dropped below a certain point. 
  \end{enumerate}
\end{enumerate}

%-----------END PASSANGER DORMS-----------

%----------BEGIN POSSIBLE DEATHS----------

\subsection{Possible Deaths}

\begin{enumerate}
  \item Lack of oxygen
  \item Freezing temperatures
  \item Sucked out into space without a space suit
  \item Sucked out into space with a space suit
  \item Shot by the captain in the head
  \item Shot by the captain in the chest
  \item Shot by the captain a second time
  \item Reavers (small random chance)
\end{enumerate}

%-----------END POSSIBLE DEATHS-----------

%----------BEGIN WALKTHROUGH----------

\section{Walkthrough}

\qq The following is a transcript of the game from start to finish following the
quickest path.

\verbatiminput{Walkthrough.txt}

%-----------END WALKTHROUGH-----------

\end{document}
